\section*{Peer-reviewed publications}

\textbf{Nadège Guiglielmoni}, Antoine Houtain, Alessandro Derzelle, Karine Van Doninck, Jean-François Flot. Overcoming uncollapsed haplotypes in long-read assemblies of non-model organisms. \textit{BMC Bioinformatics} (2021).

Lyam Baudry, \textbf{Nadège Guiglielmoni}, Hervé Marie-Nelly, Alexandre Cormier, Martial Marbouty, Komlan Avia, Yann Loe Mie, Olivier Godfroy, Lieven Sterck, J Mark Cock, Christophe Zimmer, Susana M Coelho, Romain Koszul. instaGRAAL: chromosome-level quality scaffolding of genomes using a proximity ligation-based scaffolder. \textit{Genome Biology} (2020).

\section*{Preprints}

Roland Faure, \textbf{Nadège Guiglielmoni}, Jean-François Flot. GraphUnzip: unzipping assembly graphs with long reads and Hi-C. \textit{bioRxiv} (2021). 

Zeyuan Chen, Özgül Doğan, \textbf{Nadège Guiglielmoni}, Anne Guichard, Michael Schrödl. The \textit{de novo} genome of the "Spanish" slug \textit{Arion vulgaris} Moquin-Tandon, 1855 (Gastropoda: Panpulmonata): massive expansion of transposable elements in a major pest species. \textit{bioRxiv} (2020). 

Paul Simion, Jitendra Narayan, Antoine Houtain, Alessandro Derzelle, Lyam Baudry, Emilien Nicolas, Rohan Arora, Marie Cariou, Corinne Cruaud, Florence Rodriguez Gaudray, Clément Gilbert, \textbf{Nadège Guiglielmoni}, Boris Hespeels, Djampa Kozlowski, Karine Labadie, Antoine Limasset, Marc Llirós, Martial Marbouty, Matthieu Terwagne, Julie Virgo, Richard Cordaux, Etienne GJ Danchin, Bernard Hallet, Romain Koszul, Jean-François Flot, Karine Van Doninck. Homologous chromosomes in asexual rotifer \textit{Adineta vaga} suggest automixis. \textit{bioRxiv} (2020).

\section*{Talks}

Roland Faure, \textbf{Nadège Guiglielmoni}, Jean-François Flot. GraphUnzip: unzipping assembly graphs with long reads and Hi-C. \textit{Journées Ouvertes en Biologie, Informatique et Mathématiques} (2021).

\textbf{Nadège Guiglielmoni}, Roland Faure, Jean-François Flot. hic2gfa:  unzipping assembly graphs with chromosome conformation capture. \textit{3D Genomics} (2020).

\textbf{Nadège Guiglielmoni}, Jean-François Flot. How to crack the genomes of non-model invertebrates: lessons from coral and rotifer genome projects. \textit{Biodiversity Genomics} (2020). 

\textbf{Nadège Guiglielmoni}, Antoine Houtain, Alessandro Derzelle, Karine Van Doninck, Jean-François Flot. Overcoming uncollapsed haplotypes in long-read assemblies of non-model organisms. \textit{Journées Ouvertes en Biologie, Informatique et Mathématiques} (2020). Best talk award.

\section*{Posters}

\textbf{Nadège Guiglielmoni}, Antoine Houtain, Alessandro Derzelle, Karine Van Doninck, Jean-François Flot. Overcoming uncollapsed haplotypes in Nanopore assemblies. \textit{London Calling} (2021).

\textbf{Nadège Guiglielmoni}, Romain Koszul, Jean-François Flot. Benchmarking Hi-C scaffolders. \textit{Journées Ouvertes en Biologie, Informatique et Mathématiques} (2019). 